Investigating Determinism of Game Engines for Autonomous Vehicle Verification

### 2020-04-29 paper/cav_determinisim_main.tex
method flowchart figure

% This was calculated by averaging the variance between all of the different runs through out the simulation time for all of the agents, then taking the square root to obtain the total mean devaiton. Note the dotted red line in the plot shows the millimeter (mm) level. Below this level we assume that the simulation variance is low enough that it would not affect our assertion checking for V\&V of AV simulations purposes, that it is sufficient to assume the tests are deterministic and repeatable. This line can be moved up or down and it is entirely up to verification engineers where they want to define the level below which tests' variance is negligibale and it is suffcient to assume that tests are deterministic.
%
\begin{figure*}[b]
    \centering
    \includegraphics[width=0.99\linewidth]{Other/Figures/MethodologyDiagram.pdf}
    \caption{Flow diagram of the methodology proposed to determine the simulation variance of a simulation.}
    \label{method_diagram}
\end{figure*}

@@

\subsubsection{Simulated Actors} \label{s:actors}

Different actor types may be handled differntly by the game engine and our investigation indicated that Carla pedestrians (termed \textit{walkers}) do not suffer from simulation variance under any conditions that were tested. However the introduction of Carla vehicles increased the simulation variance of the pedestrian-only test by 12 orders of magnitude. As such, all actors that could be included in any future simulation should be tested, including any non-standard Carla or bespoke actors.
%
Actor paths should hard-coded in a number of different tests that explore; no collisions, collisions between actors, and potentially collisions between actors and static scenery if this is likely to occur in the simulation.

@@

\subsection{Internal Settings}
The settings internal to the game engine or other simulation environment should be set to ensure a fixed physics time step, $dt$. If using Carla a small fixed value, say $0.05s$, can be set by using the following: \texttt{setting.fixed\_delta\_seconds = 0.05}, whereas in Unity the default fixed time step is set to $0.02s$\footnote{\url{https://docs.unity3d.com/ScriptReference/MonoBehaviour.FixedUpdate.html}}. In Carla, synchronous mode must be used to allow communication to external controllers which ensures no sensor data are passed out of order to the simulator which is particularly important if a complex ego controller is used~\cite{carla_sim_config}. 
%
The use of random numbers must be controlled through the use of fixed seeds which might be used to control variations of background effects, e.g. weather patterns, or the navigation of random pedestrian actors, external vehicle controllers or other clients connected to the simulation environment. 
%
Actors that navigate through the environment should use a fixed navigation mesh.

@@

\subsubsection{Scheduling Policy}
We hypothesise that thread scheduling may be a major contributor to the non-deterministic results found in the empirical study. However, fine control over the scheduling policy and thread execution order may be non-trivial. Such policies are defined by the operating system and may execute threads with equal priority. In such a case, all tasks non-essential to the simulator should be terminated to prevent interruption to the simulator.

>>>>

% This was calculated by averaging the variance between all of the different runs through out the simulation time for all of the agents, then taking the square root to obtain the total mean devaiton. Note the dotted red line in the plot shows the millimeter (mm) level. Below this level we assume that the simulation variance is low enough that it would not affect our assertion checking for V\&V of AV simulations purposes, that it is sufficient to assume the tests are deterministic and repeatable. This line can be moved up or down and it is entirely up to verification engineers where they want to define the level below which tests' variance is negligibale and it is suffcient to assume that tests are deterministic.
%
\begin{figure*}[b]
    \centering
    \includegraphics[width=0.99\linewidth]{Other/Figures/Methodology_Diagram_v4.pdf}
    \caption{Flow diagram of the methodology proposed to determine the simulation variance of a simulation.}
    \label{method_diagram}
\end{figure*}

@@

\subsubsection{Actors} \label{s:actors}

Different actor types may be handled differntly by the game engine and our investigation indicated that Carla pedestrians (termed \textit{walkers}) do not suffer from simulation variance under any conditions that were tested. However the introduction of Carla vehicles increased the simulation variance of the pedestrian-only test by 12 orders of magnitude. As such, all actors that could be included in any future simulation should be tested, including any non-standard Carla or bespoke actors.
%
\subsubsection{Trajectories and Collisions} 
Actor paths should hard-coded in a number of different tests that explore; no collisions, collisions between actors, and potentially collisions between actors and static scenery if this is likely to occur in the simulation.

@@

\subsection{Simulator Settings}
The settings internal to the game engine or other simulation environment should be set to ensure a fixed physics time step, $dt$. If using Carla a small fixed value, say $0.05s$, can be set by using the following: \texttt{setting.fixed\_delta\_seconds = 0.05}, whereas in Unity the default fixed time step is set to $0.02s$\footnote{\url{https://docs.unity3d.com/ScriptReference/MonoBehaviour.FixedUpdate.html}}. In Carla, synchronous mode must be used to allow communication to external controllers which ensures no sensor data are passed out of order to the simulator which is particularly important if a complex ego controller is used~\cite{carla_sim_config}. 
%
The use of random numbers must be controlled through the use of fixed seeds which might be used to control variations of background effects, e.g. weather patterns, or the navigation of random pedestrian actors, external vehicle controllers or other clients connected to the simulation environment. 
%
Actors that navigate through the environment should use a fixed navigation mesh.

@@

\subsubsection{Scheduling}
We hypothesise that thread scheduling may be a major contributor to the non-deterministic results found in the empirical study. However, fine control over the scheduling policy and thread execution order may be non-trivial. Such policies are defined by the operating system and may execute threads with equal priority. In such a case, all tasks non-essential to the simulator should be terminated to prevent interruption to the simulator.
